---
title: "Test Apply"
output: html_document
date: "2023-07-09"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


#1. Setup configuration


```{r}
devtools::load_all()
setupWorkspace(filePath="/home/ubuntu/TFG/R/distR/configuration.txt")
```


```{r}
library(datasets)
data(iris)
iris<-iris[,c(1:3)]
data<-iris
```
#Margin=1
Execute distributed apply margin=1 return dim=1
```{r}
funct<-function(data,c1,c2){return(mean(data)+c1+c2)}
dat<-matrix(c(1:10),ncol=2)
token<-distApply(dat,FUN=funct,MARGIN=1,c1=1,c2=2)
c<-getResults(token)
ap<-apply(dat,FUN=funct,MARGIN=1,c1=1,c2=2)
identical(unname(c),apply(dat,FUN=funct,MARGIN=1,c1=1,c2=2))
```
```{r}
funct<-function(data,c1,c2){return(mean(data)+c1+c2)}
dat<-matrix(c(1:10),nrow=2)
token<-distApply(dat,FUN=funct,MARGIN=1,c1=1,c2=2)
c<-getResults(token)
ap<-apply(dat,FUN=funct,MARGIN=1,c1=1,c2=2)
identical(unname(c),apply(dat,FUN=funct,MARGIN=1,c1=1,c2=2))
```

```{r}
funct<-function(data,c1,c2){return(mean(data)+c1+c2)}
token<-distApply(data,FUN=funct,MARGIN=1,c1=1,c2=2)
c<-getResults(token)
ap<-apply(data,FUN=funct,MARGIN=1,c1=1,c2=2)
identical(unname(c),apply(data,FUN=funct,MARGIN=1,c1=1,c2=2))
```
Execute distributed apply margin=1 return dim>1
```{r}
funct<-function(data,c1,c2){return(c(data[1],c1+c2))}
dat<-matrix(c(1:12),ncol=3)
token<-distApply(dat,FUN=funct,MARGIN=1,c1=1,c2=2)
c<-getResults(token)
ap<-apply(dat,FUN=funct,MARGIN=1,c1=1,c2=2)
identical(unname(c),unname(apply(dat,FUN=funct,MARGIN=1,c1=1,c2=2)))
```
```{r}
funct<-function(data,c1,c2){return(c(data[1],c1+c2))}
token<-distApply(data,FUN=funct,MARGIN=1,c1=1,c2=2)
c<-getResults(token)
ap<-apply(data,FUN=funct,MARGIN=1,c1=1,c2=2)
identical(unname(c),unname(apply(data,FUN=funct,MARGIN=1,c1=1,c2=2)))
```
#Margin=2
Execute distributed apply margin=2 return dim=1
```{r}
funct<-function(data,c1,c2){return(mean(data)+c1+c2)}
dat<-matrix(c(1:10),ncol=2)
token<-distApply(dat,FUN=funct,MARGIN=2,c1=1,c2=2)
c<-getResults(token)
ap<-apply(dat,FUN=funct,MARGIN=2,c1=1,c2=2)
identical(unname(c),apply(dat,FUN=funct,MARGIN=2,c1=1,c2=2))
```
```{r}
funct<-function(data,c1,c2){return(mean(data)+c1+c2)}
dat<-matrix(c(1:10),nrow=2)
token<-distApply(dat,FUN=funct,MARGIN=2,c1=1,c2=2)
c<-getResults(token)
ap<-apply(dat,FUN=funct,MARGIN=2,c1=1,c2=2)
identical(unname(c),apply(dat,FUN=funct,MARGIN=2,c1=1,c2=2))
```

```{r}
funct<-function(data,c1,c2){return(mean(data)+c1+c2)}
token<-distApply(data,FUN=funct,MARGIN=1,c1=1,c2=2)
c<-getResults(token)
ap<-apply(data,FUN=funct,MARGIN=1,c1=1,c2=2)
identical(unname(c),apply(data,FUN=funct,MARGIN=1,c1=1,c2=2))
```
Execute distributed apply margin=1 return dim>1
```{r}
funct<-function(data,c1,c2){return(c(data[1],c1+c2))}
dat<-matrix(c(1:12),ncol=3)
token<-distApply(dat,FUN=funct,MARGIN=2,c1=1,c2=2)
c<-getResults(token)
ap<-apply(dat,FUN=funct,MARGIN=2,c1=1,c2=2)
identical(unname(c),unname(apply(dat,FUN=funct,MARGIN=2,c1=1,c2=2)))
```
```{r}
funct<-function(data,c1,c2){return(c(data[1],c1+c2))}
token<-distApply(data,FUN=funct,MARGIN=1,c1=1,c2=2)
c<-getResults(token)
ap<-apply(data,FUN=funct,MARGIN=1,c1=1,c2=2)
identical(unname(c),unname(apply(data,FUN=funct,MARGIN=1,c1=1,c2=2)))
```

#Margin=c(1,2)

Execute distributed apply margin=c(1,2) return dim=1
```{r}
funct<-function(data,c1,c2){return(mean(data)+c1+c2)}
dat<-matrix(c(1:10),ncol=2)
token<-distApply(dat,FUN=funct,MARGIN=c(1,2),c1=1,c2=2)
c<-getResults(token)
ap<-apply(dat,FUN=funct,MARGIN=c(1,2),c1=1,c2=2)
identical(unname(c),apply(dat,FUN=funct,MARGIN=c(1,2),c1=1,c2=2))
```

```{r}
funct<-function(data,c1,c2){return(mean(data)+c1+c2)}
dat<-matrix(c(1:10),ncol=2)
token<-distApply(data,FUN=funct,MARGIN=c(1,2),c1=1,c2=2)
c<-getResults(token)
ap<-apply(data,FUN=funct,MARGIN=c(1,2),c1=1,c2=2)
identical(unname(c),apply(data,FUN=funct,MARGIN=c(1,2),c1=1,c2=2))
```

Execute distributed apply margin=c(1,2) return dim>1
```{r}
funct<-function(data,c1,c2){return(c(data[1],c1+c2))}
dat<-matrix(c(1:12),ncol=3)
token<-distApply(dat,FUN=funct,MARGIN=c(1,2),c1=1,c2=2)
c<-getResults(token)
ap<-apply(dat,FUN=funct,MARGIN=c(1,2),c1=1,c2=2)
identical(unname(c),unname(apply(dat,FUN=funct,MARGIN=c(1,2),c1=1,c2=2)))
```



```{r}
funct<-function(data,c1,c2){return(c(data[1],c1+c2))}
token<-distApply(data,FUN=funct,MARGIN=c(1,2),c1=1,c2=2)
c<-getResults(token)
ap<-apply(data,FUN=funct,MARGIN=c(1,2),c1=1,c2=2)
identical(unname(c),unname(apply(data,FUN=funct,MARGIN=c(1,2),c1=1,c2=2)))
```
#Margin=c(2,1)

Execute distributed apply margin=c(2,1) return dim=1
```{r}
funct<-function(data,c1,c2){return(mean(data)+c1+c2)}
dat<-matrix(c(1:10),ncol=2)
token<-distApply(dat,FUN=funct,MARGIN=c(2,1),c1=1,c2=2)
c<-getResults(token)
ap<-apply(dat,FUN=funct,MARGIN=c(2,1),c1=1,c2=2)
identical(unname(c),apply(dat,FUN=funct,MARGIN=c(2,1),c1=1,c2=2))
```

```{r}
funct<-function(data,c1,c2){return(mean(data)+c1+c2)}
dat<-matrix(c(1:10),ncol=2)
token<-distApply(data,FUN=funct,MARGIN=c(2,1),c1=1,c2=2)
c<-getResults(token)
ap<-apply(data,FUN=funct,MARGIN=c(2,1),c1=1,c2=2)
identical(unname(c),apply(data,FUN=funct,MARGIN=c(2,1),c1=1,c2=2))
```

Execute distributed apply margin=c(2,1) return dim>1
```{r}
funct<-function(data,c1,c2){return(c(data[1],c1+c2))}
dat<-matrix(c(1:12),ncol=3)
token<-distApply(dat,FUN=funct,MARGIN=c(2,1),c1=1,c2=2)
c<-getResults(token)
ap<-apply(dat,FUN=funct,MARGIN=c(2,1),c1=1,c2=2)
identical(unname(c),unname(apply(dat,FUN=funct,MARGIN=c(2,1),c1=1,c2=2)))
```



```{r}
funct<-function(data,c1,c2){return(c(data[1],c1+c2))}
token<-distApply(data,FUN=funct,MARGIN=c(2,1),c1=1,c2=2)
c<-getResults(token)
ap<-apply(data,FUN=funct,MARGIN=c(2,1),c1=1,c2=2)
identical(unname(c),unname(apply(data,FUN=funct,MARGIN=c(2,1),c1=1,c2=2)))
```



